Monty Hall Constraints

### 2021-03-18 quant_estimate/constraints_log_montyhall.tex
WIP : Monty Hall

Path : 14
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	!((!(car_door_sym == 1) && !(choice_pse_var_sym == 1)))
	(!(car_door_sym == 2) && !(choice_pse_var_sym == 2))
	!(door_switch_pse_var_sym == 0)
	choice_pse_var_sym == 1
	!(car_door_sym == 3)
	\end{minted}
\end{document}

>>>>

Path : 14
	0 <= door_switch_pse_var_sym
	door_switch_pse_var_sym <= 1
	0 <= choice_pse_var_sym
	choice_pse_var_sym <= 3
	0 <= car_door_sym
	car_door_sym <= 3
	!((!(car_door_sym == 1) && !(choice_pse_var_sym == 1)))
	(!(car_door_sym == 2) && !(choice_pse_var_sym == 2))
	!(door_switch_pse_var_sym == 0)
	choice_pse_var_sym == 1
	!(car_door_sym == 3)
	\end{minted}

We present the observations for the \texttt{Monty Hall}. \\ \\ \\

\begin{minted}{c}
-  For door_switch == 0
	(P(win) >= 0.5) passes,

-  For door_switch == 1 
	(P(win) >= 0.5) fails,

-  When count(door_switch == 0) == count(door_switch == 1) 
	(P(win) <= 0.5) fails 
	(P(win) >= 0.5) passes.

-  When ever count(door_switch == 0) < count(door_switch == 1) with bias 
		Higher probability of winning when the person switches.
			(P(win) <= 0.5) fails :

	Fail : P(choice == car_door)  :  0.860216  
	Fail : P(choice == car_door)  :  0.520136  
	Fail : P(choice == car_door)  :  0.780963   
		...

-  When ever count(door_switch == 0) > count(door_switch == 1)  with bias
		(P(win) >= 0.5) fails :

	Fail : P(choice == car_door)  :  0.499620   
	Fail : P(choice == car_door)  :  0.379960  
	Fail : P(choice == car_door)  :  0.139769   
		...
\end{minted}

\end{document}
